Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2016-05-03 cikm2016/cikm_dateparse.tex
Back to 10 pages.

\maketitle
\begin{abstract}
Interactive visual analytics is an effective approach for the timely analysis of big data. Users who are already engaged in interactive data analysis prefer to stay in the visualization environment for unavoidable data cleaning and preparation tasks in order to preserve their analytic flow. This has led visualization environments to include simple data preparation functions such as scalar parsing, pattern matching and categorical binning. One common scalar parsing task is extracting date and time data from string representations. Several relational database management systems (RDBMSs) include date parsing ``mini-languages'' to cover the wide range of possible formats, but analysis of user data from one visualization system shows that the parsing language syntax is difficult for users to master without disturbing their analytic flow.

>>>>

\maketitle

\begin{abstract}
Interactive visual analytics is an effective approach for the timely analysis of data. Users who are engaged in interactive data analysis prefer staying in the visualization environment for unavoidable data cleaning and preparation tasks to preserve their analytic flow. This has led visualization environments to include simple data preparation functions such as scalar parsing, pattern matching and categorical binning. A common scalar parsing task is extracting date and time data from string representations. Several relational database management systems (RDBMSs) include date parsing ``mini-languages'' to cover the wide range of possible formats, but analysis of user data from one visualization system shows that the parsing language syntax is difficult for users to master without disturbing their analytic flow.
